---
title: "Geometry Workflows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Geometry Workflows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidycops)
```

## Standardized geometry (recommended)

For non-Dallas comparable analysis, use `as_sf = TRUE`. This builds point
geometry from `std_longitude`/`std_latitude` in EPSG:4326.

```{r eval = FALSE}
sf_std <- get_standardized_incidents(
  city = "seattle",
  last_n_days = 7,
  output = "comparable",
  as_sf = TRUE,
  limit = 5000
)
```

You can also use the same behavior through `get_incidents()`:

```{r eval = FALSE}
sf_cmp <- get_incidents(
  city = "seattle",
  view = "comparable",
  last_n_days = 7,
  as_sf = TRUE,
  limit = 5000
)
```

## Dallas legacy geometry

Dallas still uses legacy projected coordinates with `convert_geo = TRUE`
(EPSG:2276).

```{r eval = FALSE}
dallas_sf <- get_incidents(
  city = "dallas",
  start_date = "2024-03-01",
  end_date = "2024-03-31",
  convert_geo = TRUE,
  limit = 2000
)
```

## Notes

- `as_sf` is ignored for `view = "city_full"` and `view = "city_raw"`.
- If coordinates are missing/invalid, `tidycops` drops those rows before
  conversion and warns.
