---
title: "Incident Views and Retrieval Modes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Incident Views and Retrieval Modes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidycops)
```

## Overview

`get_incidents()` supports four output views for non-Dallas city adapters.

- `view = "both"`: city-native fields plus standardized `std_*` columns
- `view = "comparable"`: only standardized `std_*` columns
- `view = "city_full"`: full city schema plus adapter metadata columns
- `view = "city_raw"`: untouched source payload rows

## Comparable view

```{r eval = FALSE}
cmp <- get_incidents(
  city = "cincinnati",
  view = "comparable",
  last_n_days = 7,
  offense = "theft",
  limit = 500
)
```

## City full view

```{r eval = FALSE}
full <- get_incidents(
  city = "houston",
  view = "city_full",
  last_n_days = 7,
  limit = 1000
)
```

## Raw payload view

```{r eval = FALSE}
raw <- get_incidents(
  city = "houston",
  view = "city_raw",
  last_n_days = 7,
  limit = 1000
)
```

## Raw convenience helper

`download_city_incidents_raw()` is a shortcut for untouched incident payloads.

```{r eval = FALSE}
raw2 <- download_city_incidents_raw(
  city = "houston",
  last_n_days = 7,
  limit = 1000
)
```

## Date window options

Use either explicit dates or a trailing window:

```{r eval = FALSE}
# Explicit range
get_incidents(city = "san_francisco", view = "comparable",
              start_date = "2026-04-01", end_date = "2026-04-07")

# Trailing range
get_incidents(city = "san_francisco", view = "comparable",
              last_n_days = 7)
```
