---
title: "Source Coverage and Caveats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Source Coverage and Caveats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidycops)
```

## Why this matters

City incident portals differ in time coverage and scope. `tidycops` tracks this
in source metadata so you can evaluate comparability before analysis.

## Source registry

```{r}
sources <- list_incident_sources()
sources
```

## Key metadata fields

- `active_from`, `active_to`: date window for a source slice
- `source_status`, `source_note`: freshness and rolling/capped behavior
- `scope_status`, `scope_note`: definition limits (for example Part I-only)

## Find feeds with caveats

```{r}
subset <- dplyr::filter(
  sources,
  source_status %in% c("rolling_window", "historical_capped") |
    scope_status != "all_incidents"
)
subset
```

## Practical workflow

1. Query `list_incident_sources(city = ...)` before pulling data.
2. Match analysis window to what the feed actually covers.
3. Keep source notes with outputs when sharing results.
