---
title: "tidycops Quickstart"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tidycops Quickstart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidycops)
```

## Why tidycops?

Public incident feeds vary by city and provider. `tidycops` gives you a single
interface for:

- discovering supported city adapters,
- pulling city-native or cross-city standardized records, and
- filtering with one consistent set of arguments.

## Discover support

```{r}
list_supported_incident_cities()
list_incident_sources()
list_standard_incident_fields()
```

## Pull comparable records

```{r eval = FALSE}
sf_recent <- get_standardized_incidents(
  city = "san_francisco",
  last_n_days = 7,
  offense_category = "larceny theft",
  as_sf = TRUE,
  limit = 500
)
```

## Pull full city schema

```{r eval = FALSE}
cincy_full <- get_incidents(
  city = "cincinnati",
  view = "city_full",
  last_n_days = 14,
  limit = 1000
)
```

## Pull untouched payload rows

```{r eval = FALSE}
houston_raw <- download_city_incidents_raw(
  city = "houston",
  last_n_days = 7,
  limit = 2000
)
```

## Next reads

- `vignette("incident-views", package = "tidycops")`
- `vignette("cross-city-comparisons", package = "tidycops")`
- `vignette("source-coverage-and-caveats", package = "tidycops")`
- `vignette("geometry-workflows", package = "tidycops")`
